### 2014-08-10 nips_rebuttal_1262.txt

Summaries (scores)
------------------
Assigned_Reviewer_15 (5): This paper is an extension of the R-CNN window proposal-based object detection algorithm of Girshick et al.'CVPR 2014. The novelty of the paper is limited but it has an interesting idea of using the output of the intermediate layers in the CNN hierarchy. The experiments are solid and demonstrate speeding-up R-CNN, at only a reasonable loss in performance. However, most of the speedup can be obtained by training a foreground-background classifier on the window proposals and processing the highest-scoring ones. The paper lacks details at multiple places needed to reproduce the results. The significance beyond the specific set-up of Girshick et al.'14 is not clear.

Assigned_Reviewer_43 (4): This paper presents several approaches to speed up the Region-based CNN. The approaches are rather heuristic and the novelty is limited. The experimental evaluations are not adequate either.

Assigned_Reviewer_9 (7): Speeding up the very slow but state-of-the-art R-CNN algorithm is of practical consequence for computer vision and the current paper offers a comprehensive and well-performing solution using a collection of suitable approaches. The paper is generally well written and experimental results are convincing.

Rebuttal
--------
We thank the reviewers for their thoughtful consideration.
We feel that the reviewers underestimated the impact of the Cascaded CNN we report, and see the need for a more clear rhetorical focus on this contribution.

Addressing specific concerns:

- "For the "Pixel gradient" method. What is the gradient computed here? Gradient with respect to the loss? What is the loss used (does it allow multiple labels per image)? Is the network applied to the whole image? How does the method deal with non-square images?"

Our method follows reference [7] (http://arxiv.org/abs/1312.6034) to the best of our knowledge. Images are resized to square and classified with an "AlexNet" CNN fine-tuned on the PASCAL VOC classification dataset with multi-label loss. At test-time, the gradient at the top is with respect to the indicator function of the max-scoring class, and is back-propagated all the way to the pixels, where it is summed across channels.

- "For the "Cascade" method. What form of the classifier is used here? Are the feature maps processed in any way before training the classifier?"

Each cascade classifier is implemented as a fully-connected layer following a linear rectification, trained with simple logistic loss using foreground/background labels (and with dropout).

- "Will the rejected regions in the cascaded CNN be re-processed? If not, its performance should be worse than the original R-CNN at the 10000 ms time allotted (see Table. 2), as the true-positives might be filtered out in the early stage."

The answer is yes, and the reviewer is correct about the implications. This is our mistake: the table entries for C-CNN methods at 10,000 ms should be blank.

- "How will the performance change if using the different batch size?"

This is an empirical question and thus a great experimental suggestion that we will execute.

- "The paper does not explain why removing certain regions using the cascaded approach can be done efficiently in the batch, on GPU. Do we lose some efficiency from not applying batch-optimized routines?"

In the very efficient implementation of CNNs we use (Caffe), there is a simple loop over each batch element in both CPU and GPU convolution code. We modify this loop to simply not perform convolution on those elements that were rejected earlier in the cascade. It's true that the memory remains needlessly occupied, but we do consider this a problem with our large-capacity GPUs.

- "If each region rejection layer is tuned to have 80% recall on positive regions, wouldn't the combination of all of them end up with less than 80% recall? Also, 80% positive recall at each stage seems too low?"

This is correct, and is an empirical question that we are running additional experiments to answer.

- "Perhaps another way of prioritizing regions by quick-to-compute score is to pick batches of regions with high scores that don't overlap too much (using non-max-suppression estimates to diversify the region set)? This is a potential alternative to the current scheme, unclear if it would help."

This is a scheme we considered but decided against, due to the additional time required to run non-maximum suppression. Also keep in mind that our region proposal mechanism does not provide confidences to regions, making non-maximum suppression only slightly more meaningful than our current random scheme.

### 2014-08-11 nips_rebuttal_1262.txt

- "For the "Cascade" method. What form of the classifier is used here? Are the feature maps processed in any way before training the classifier?"

Each cascade classifier is implemented as a fully-connected layer following a linear rectification, trained with simple logistic loss using foreground/background labels (and with dropout).

- "Will the rejected regions in the cascaded CNN be re-processed? If not, its performance should be worse than the original R-CNN at the 10000 ms time allotted (see Table. 2), as the true-positives might be filtered out in the early stage."

The answer is no, they will not be re-processed, and the reviewer is correct about the implications. This is our mistake: the table entries for C-CNN methods at 10,000 ms should be blank.

@@

- "How will the performance change if using the different batch size?"

This is an empirical question and thus a great experimental suggestion that we will execute.

- "The paper does not explain why removing certain regions using the cascaded approach can be done efficiently in the batch, on GPU. Do we lose some efficiency from not applying batch-optimized routines?"

In the very efficient implementation of CNNs we use (Caffe), there is a simple loop over each batch element in both CPU and GPU convolution code. We modify this loop to simply not perform convolution on those elements that were rejected earlier in the cascade. It's true that the memory remains needlessly occupied, but we do not consider this a problem with large-capacity GPUs.

@@

- "If each region rejection layer is tuned to have 80% recall on positive regions, wouldn't the combination of all of them end up with less than 80% recall? Also, 80% positive recall at each stage seems too low?"

This is correct, with a caveat: the thresholds are trained on a dataset of equal proportion positive/negative examples, while the actual dataset has much more negative than positive examples. Regardless, this is an empirical question that we are running additional experiments to answer.

### 2014-08-11 evaluation.tex
removing everything about p-rcnn; restructuring method section

The R-CNN software was used as available in June 2014\footnote{\url{https://github.com/rbgirshick/rcnn}}.
That software relies on Selective Search \cite{Uijlings-IJCV-2013} region proposals.
Different images are proposed different numbers of regions.
\autoref{fig:roi_hist_and_gradient} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
An additional parameter is the size of each batch of regions that goes through the CNN.
We set batch size to 100 regions, and observe that it takes on average 500 ms to process them with the CNN.
In all experiments, we use Ubuntu 12.04, Intel i5 3.2GHz CPU, and NVIDIA Tesla K40 GPU.

The scoring function for the Region Statistics, Pixel Gradient, and Pyramid R-CNN features is trained by a logistic regression classifier onto the supervised signal of region overlap with ground truth on the validation dataset.
The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.

@@

\begin{figure}[ht]
\centering
\begin{subfigure}[b]{0.52\linewidth}
    \includegraphics[width=\linewidth]{figures/_apvst_final.pdf}
    \caption{mAP vs. time allotted for detection}\label{fig:apvst}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{figures/_speedup_final_abs.pdf}
    \caption{mAP vs. speed-up factor}\label{fig:speedup}
\end{subfigure}
\caption{
Results on the PASCAL VOC 2007 dataset.
(a) On the left-hand mAP vs. Time plot, we can compare APs at a given allotted time point.
For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
(b) On the right-hand speed-up plot, we can compare speed-ups at a given mAP point.
For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
}\label{fig:voc2007_results}
\end{figure}

\begin{table}[ht]
\centering
\caption{
Full table of AP vs. Time results on PASCAL VOC 2007.
Best performance for each time point is in bold.
}\label{tab:results}
\small{
\include{results_table}
}
\end{table}

\subsection{Experiments}
\begin{description}
  \item[Original] \hfill \\
  The original order of the Selective Search regions of interest.
  This order is influenced by the hierarchical segmentation of their method, and so has sequences of highly overlapping regions.
  \item[Random] \hfill \\
  A completely blind permutation of the original order.
  \item[Region Selection] \hfill \\
  The region statistics feature from \autoref{sec:region} is always used.
  Additionally, we consider either the Pixel Gradient and the Pyramid R-CNN features.
  These two features have a \emph{setup time}: the gradient forward-back propagation takes 20 ms, and the Pyramid R-CNN takes a whopping 800 ms.
  \item[Cascaded CNN] \hfill \\
  The Cascaded CNN model, as described in \autoref{sec:ccnn}.
  The first experiment (C-CNN) takes batches of regions in a random order.
  The next two experiments also make use of the Region Selection methodology, and the two fast features of Pixel Gradient and the Pyramid R-CNN.
\end{description}

@@

At 600 ms, C-CNN method have had more than one batch go through, and the Region Selection is giving it a lead over the simple C-CNN.
Both method are better than the baseline non-cascaded methods for this entire duration.
This changes once the Pyramid R-CNN has time to compute and to run through a few batches.
The later times show best performance from the Region Selection with that feature.

>>>>

The scoring function for the quick-to-compute features is trained by a logistic regression classifier onto the max PASCAL overlap with any ground truth window on the validation dataset.
The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.

The R-CNN software was used as available in June 2014.
\footnote{\url{https://github.com/rbgirshick/rcnn}}
That software relies on Selective Search \cite{Uijlings-IJCV-2013} region proposals.
Different images are proposed different numbers of regions.
\autoref{fig:roi_hist_and_gradient} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
An additional parameter is the size of each batch of regions that goes through the CNN.
We set batch size to 100 regions, and observe that it takes on average 500 ms to process them with the CNN.
In all experiments, we use Ubuntu 12.04, Intel i5 3.2GHz CPU, and NVIDIA Tesla K40 GPU.

@@

\input{voc2007_fig}

\input{voc2007_table}

\subsection{Experiments}
\begin{description}
  \item[Original] \hfill \\
  The original order of the Selective Search regions of interest.
  This order is influenced by the hierarchical segmentation of their method, and so has sequences of highly overlapping regions.

  \item[Random] \hfill \\
  A completely blind permutation of the original order.

  \item[Region Selection] \hfill \\
  The region statistics feature from \autoref{sec:region} is always used.
  Additionally, we consider the Pixel Gradient feature, with \emph{setup time} of the gradient forward-back propagation of 20 ms.

  \item[Cascaded CNN] \hfill \\
  The Cascaded CNN model, as described in \autoref{sec:ccnn}.
  The first experiment (C-CNN) takes batches of regions in a random order.
  The next two experiments also make use of the Region Selection methodology with the quick-to-compute feature.
\end{description}

@@

At 600 ms, C-CNN method have had more than one batch go through, and the Region Selection is giving it a lead over the simple C-CNN.
Both method are better than the baseline non-cascaded methods for this entire duration.

### 2014-08-11 introduction.tex
removing everything about p-rcnn; restructuring method section

Multi-layered convolutional models (CNNs) have recently demonstrated impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
While convolutional models are inherently efficient to implement, as convolution itself is a parallelizable and long studied computational primitive, the amount of work to perform complete inference at all candidate region windows is considerable.

The standard method for quickly applying a CNN to a large number of candidate regions is to restrict the regions to lie in a regular scale-space pyramid.
With this restriction, the CNN can efficiently compute features for all regions using convolution.
This approach was used in classical CNN-based detection systems, as well as recent approaches such as OverFeat \cite{Sermanet-ICLR-2014}.
The recently proposed Regions with CNN features (R-CNN), in contrast, allows for more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows without sharing computation.
While R-CNN has leading performance on PASCAL and ImageNet detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (not counting region generation).

In this paper, we investigate a novel approach for speeding up R-CNN by proposing a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection).
We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.

We also consider a variety of strong baselines for speeding up R-CNN.
One of these baselines is a novel approach that approximates R-CNN by first building a feature pyramid, which is inherently efficient, and then using the pyramid to share features between overlapping region proposals.
While this methods performs quite well on its own, we show that our Cascaded CNN provides a better speed-up with a simpler approach.

%Existing detection schemes, including R-CNN and OverFeat, are generally relatively naive in terms of the temporal properties of their inference.
%They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
%In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
%(Or when time is considered a costly resource.)
%We build on the work of \cite{Karayev-NIPS-2012}, who considered time-sensitive feature selection in a classification paradigm, but extend the model to be relevant to contemporary detector settings, and to include spatial reasoning.

%Our model yields novel forms of ``cascaded''-style processing for such detectors, where large amounts of computation is pruned when it is deemed redundant, or likely unproductive.
%We consider both static and dynamic policies for such behavior, and features based on low-level cues and mid-level ConvNet features.
%We focus on speeding up the R-CNN framework, but our work is relevant to any detector that operates a relatively expensive function over a set of candidate locations.
%Our model implicily learns to look elsewhere when a nearby region is already examined, and to look above a motorbike for a possible person; it generalized well known principles of non-maximal suppression and inter-task context.

%We consider three specific mechanisms, which are independently and jointly valuable.
%[[ 1) dense eval.; 2) cascade; 3) dynamic ]].
%Together we call these ``Timely'' methods for object detection, hence the title of our paper.

We discuss related work in \autoref{sec:related}, cover all parts of our proposed method in \autoref{sec:method}, and present evaluation results on the PASCAL VOC in \autoref{sec:evaluation}.

>>>>

Multi-layered convolutional models (CNNs) have recently demonstrated impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object classification data to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
While convolutional models are efficient to implement due to the availability of high-performance primitives, the amount of work to perform complete inference at all candidate region windows is still considerable.

The standard method for quickly applying a CNN to a large number of candidate regions is to restrict the regions to lie in a regular scale-space pyramid.
With this restriction, the CNN can efficiently compute features for all regions using convolution.
This approach was used in classical CNN-based detection systems as well as recent approaches such as OverFeat \cite{Sermanet-ICLR-2014}.
The recently proposed Regions with CNN features (R-CNN), in contrast, allows for more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows without sharing computation.
While R-CNN has leading performance on PASCAL and ImageNet detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (following a separate region generation step).

In this paper, we investigate a novel approach for speeding up R-CNN and propose a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection datasets).
We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.
We also consider a variety of strong baselines for speeding up R-CNN.

### 2014-08-11 method.tex
Final touches
removing everything about p-rcnn; restructuring method section

We consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found, based on inference from relatively lightweight features.  We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can provide some signal that is useful to prioritize regions, but that those are relatively weak.

Features based on convolutional mid-level primitives are more powerful, as they are directly related to our final detector.  We consider approximate measures computed from a grid of mid-level features; this proves to be a powerful signal, and provides a clear boost when the time required to compute that feature is not considered.    But even with a fast image pyramid to compute them globally for all regions, the time required is unfortunately large enough to significantly dilute their impact.

What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.  We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a ``Timely'' approach to the detection computation.

We first review the base model that our work is derived from, the R-CNN method, in the following subsection.  We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.  We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.  Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or expoit more costly mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.

\subsection{Base model}

We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs).
ROIs are taken in batches: transformed to canonical size, and classified with a CNN, obtaining multi-class scores for each region.
After all batches have been scored, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.

We start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
We then select a batch of highly-scoring ROIs and classify them with the CNN -- which can additionally be sped up with cascaded structure.
After the batch is scored, we optionally re-score the remaining ROIs, and repeat the process until we're either out of time, or out of regions.
\autoref{fig:combined} summarizes the process.

As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
This process of region selection does not reject regions flat out, but reorders them to be processed later.

We first tried to simply sort the regions by score and take batches in that sorted order.
Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
Guided by this intuition, we consider a more dynamic approach to region selection:
we put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/rcnn.pdf}
\caption{
R-CNN architecture: image regions are cropped, resized, and each one fed through a CNN with classification layers.
The classifier outputs are post-processed to give the final detections.
}\label{fig:rcnn}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/combined.pdf}
\caption{
Our method scores each region of interest with a fast feature (we evaluate several), allowing us to pick promising regions first.
The regions are classified with the original CNN, or a sped-up Cascade-CNN.
The properties of the regions can play a role in selecting the next batch of regions.
}\label{fig:combined}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Region statistics}\label{sec:region}
For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions.
We compute a very simple feature for each ROI: its normalized location,
its scale($\sqrt{\text{width} \times \text{height}}$),
aspect ratio ($\log \sqrt{\text{width} / \text{height}}$),
and normalized counts of overlapping regions, at different PASCAL overlap thresholds (0, 0.2, 0.6).

This simple feature works suprisingly well for filtering regions to process first, and is always included in concatenation with the more complex features that are described next.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CNN pixel gradient computation}\label{sec:gradient}

One fast-to-compute feature we consider for the preliminary featurization of ROIs is the pixel gradient, back-propagated throgh the classifier CNN applied to the whole image.
This gradient corresponds to a kind of saliency map onto the image \cite{Simonyan-ICLR-2014}, and can therefore be used to evaluate ROIs.

We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
Accordingly, we implement a cross-entropy loss layer to train a simple multi-label classifier with binary vector.

This pixel-wise gradient can be seen as a first-order approximation to the weight of a pixel in the classification output.
To compute it, we first run the CNN forward from image input to the prediction layer.
Back-propagating through the model and a last backward pass to the input gives the pixel-wise gradient.
A couple of example images are shown in \autoref{fig:gradient}.

We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
For each region to be evaluated, we compute the total gradient sum, sums for each of the corners, and proportions of in-region vs. out-of-region sums.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pyramid amortized R-CNN}\label{sec:dense}

Another fast ROI featurization we consider is a variant of R-CNN that processes the whole image, at multiple scales, with the CNN up to the topmost non-fully-connected layer.
We call this multiscale CNN output a ``feature pyramid''.
As \autoref{fig:dense_rcnn} shows, ROIs are then cropped from the feature pyramid at the best matching scale, warped to a canonical size, and classified.
ROIs are highly overlapping, but their featurization is shared through the pyramid, amortizing its construction cost.
This doesn't work as well as the original R-CNN system, but is much faster, and can therefore be used as the fast feature for the dynamic region selection.

% \subsubsection{Design choices}

We explored a variety of choices while designing Pyramid R-CNN.
We tried using a single scale or a pyramid with 7 levels each separated by a scale factor of $2^{-1/2}$.
For warping, we experimented with canonical sizes of $s \times s$, for $s \in \{5,6,7\}$ and resampling with nearest neighbor or bilinear interpolation.
We also tried two variants of the feature pyramid: the raw feature pyramid or one where each level is max pooled with a $3 \times 3$ pooling window run at a stride of $1$ (to avoid subsampling).

\autoref{tab:prcnn} shows mAP performance on PASCAL VOC 2007 test for these various choices.
The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
The first level of our pyramid is computed from a $1713 \times 1713$ pixel image, which yields a $108 \times 108$ cell feature map.
The gold standard (non-pyramid) R-CNN performance using the same non-fine-tuned CNN is 44.2\% mAP.
Our best result with Pyramid R-CNN is slightly worse, at 41.9\%.

To map a ROI $R$ into the pyramid, we start by computing an ``optimal'' scale defined by $\alpha^* = 227/\min(h,w)$, where $h$ and $w$ are image height and width of $R$.
We then find the nearest level in the pyramid: $l^* = \textrm{argmin}_l |\log(\alpha_l) - \log(\alpha^*)|$, where $\alpha_l$ is the scale factor for pyramid level $l$.
This procedure approximates the scale that R-CNN would use, since it operates on $227$ pixel inputs.

\begin{table}[ht]
\centering
\caption{
    Pyramid R-CNN design choices, vs mAP performance.
    We additionally show two best and two worst performing classes.
}\label{tab:prcnn}
\small{
\input{pyra_rcnn_table}
}
\end{table}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
\caption{
Post R-CNN architecture: the whole image is fed through a CNN up to the highest pooling layer.
Regions are cropped from that layer at the best matching scale, resized, and classified.
}\label{fig:dense_rcnn}
\end{center}
\end{figure}

@@

Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
It would be useful to quickly reject these regions, without expending the full amount of computation on them. Since most of the time is spent in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions. These reject layers were trained using the corresponding fine-tuned CNN.

The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to reject the region since it is background.
For our purpose, the reject layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background. The last classification layer still outputs the full multi-class scores for the surviving regions.

To set the thresholds we took a sample of 140K regions from the images in the validation set containing positive and negative examples. Then we set the threshold for the rejector after first layer to have 0.8 recall on the positive regions. Similarly we set the threshold in for the rejector after the second layer, using the regions that pass the first rejector, to maintain a 0.8 recall on positive regions. And finally we set the threshold for the rejector after the third layer, using the regions that pass the first two rejectors, to maintain a 0.8 recall on positive regions. After every rejection layer the precision on positive regions increase, going from 0.38 to 0.74, while maintaining a recall of 0.8.

@@

Therefore the expected ``lifetimes'' of regions rejected after layer 1, layer 2, layer 3 and those not rejected are  0.15, 0.35, 0.5, 1.0 of the total time taken per region (~1.7 ms).

At test time, we observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch. We multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
\caption{
The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
}\label{fig:ccnn}
\end{center}
\end{figure}

>>>>

We first consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found early, based on inference from relatively lightweight features.
We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can effectively prioritize regions.

We take the R-CNN \cite{Girshick-CVPR-2014} method as our point of departure.
As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), which are transformed to canonical size, and classified with a CNN, obtaining multi-class scores for each region.
After all batches of ROIs have been scored, they are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.

As summarized in \autoref{fig:combined}, we begin with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
We then select a batch of highly-scoring ROIs and classify them with the CNN -- which is additionally sped up with cascaded structure.
After the batch is scored, we optionally re-score the remaining ROIs, and repeat the process until either time or regions are depleted.

The quick-to-compute feature is used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
This process of region selection does not reject regions flat out, but reorders them to be processed later.

We found that simply sorting the regions by score and taking batches in that sorted order results in poor performance, and can be worse than taking regions in an entirely random order, as the highest scoring regions may be highly overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
Instead, we put regions in random order, set a threshold for the quick-to-compute feature such that only half of the unprocessed regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.

\input{rcnn_fig}

\input{combined_fig}

\subsection{Quick-to-compute feature}

\paragraph{Region statistics}\label{sec:region}
For the first source of information, we consider statistics about ROI location and overlap with other regions.
For each ROI, we compute: its normalized location, its scale($\sqrt{\text{width} \times \text{height}}$), aspect ratio ($\log \sqrt{\text{width} / \text{height}}$), and normalized counts of overlapping regions, at several PASCAL overlap thresholds (0, 0.2, 0.6).

This simple feature works suprisingly well for filtering regions to process first.
In concatenation, we also consider the \emph{pixel gradient}, back-propagated throgh a classification CNN applied to the whole image.
This feature corresponds to a kind of saliency map, giving an estimate of the importance of each pixel to the final classification of the image.

Our method follows \cite{Simonyan-ICLR-2014} to the best of our knowledge.
Images are resized to square and classified with an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN fine-tuned on the PASCAL VOC classification dataset with multi-label loss.
(Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.)
At test-time, the gradient at the top is with respect to the indicator function of the max-scoring class, and is back-propagated all the way to the pixels, where it is summed across channels.
A couple of example images are shown in \autoref{fig:roi_hist_and_gradient}.

We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
For each region to be evaluated, we compute the image-normalized gradient sum, sums for each of four corners, and ratio of in-region vs. out-of-region sums.

@@

Most ROIs that are scored in R-CNN do not contain any object of interest.
It would be useful to quickly reject these regions, without expending the full amount of computation on them.

The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep processing the input with the next layer.
Each reject layer is implemented as a fully-connected layer following a linear rectification, trained with dropout using logistic loss on foreground/background labels.
We set the reject thresholds to maintain at last 80\% recall at each stage, using a large sample of regions from images in the validation set containing positive and negative examples in equal proportion.

In the efficient implementation of CNNs we use (Caffe), there is a simple loop over each batch element in both CPU and GPU convolution code.
We modify this loop to simply not perform convolution on those elements that were rejected earlier in the cascade.
\footnote{While memory remains occupied in this scheme, we do not consider this a problem.}

Since most of the time is spent in the convolutional layers, we introduce a reject option after \texttt{pool1}, \texttt{pool2}, and \texttt{conv3}.
The last classification layer still outputs the full multi-class scores for the surviving regions.

@@

Therefore the expected ``lifetimes'' of regions rejected after layer 1, layer 2, and layer 3 are  0.15, 0.35, and 0.5 of the total time taken per region.

\input{ccnn_fig}

### 2014-08-11 related_work.tex
removing everything about p-rcnn; restructuring method section

The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} .

These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014}, or deriving a CNN-based window sampling scheme \cite{Simonyan-ICLR-2014}.
All these method have a fixed strategy and are unable to adapt their computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.

\paragraph{Cascaded detection}\label{cascaded-detection}
Detection cascades \cite{Viola2004,Felzenszwalb-CVPR-2010} are a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers. This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}. Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade} as well as a boosted cascade trained on CNN features \cite{Zou-CVPR-2014}. While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,dulac2014}.
In particular, we combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.

>>>>

The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{Deng-CVPR-2009} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-BMVC-2014,Simonyan-ICLR-2014,Erhan-CVPR-2014,Sermanet-ICLR-2014} .

These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-BMVC-2014,Sermanet-ICLR-2014}, or deriving a CNN-based window sampling scheme \cite{Simonyan-ICLR-2014}.

\paragraph{Cascaded detection}\label{cascaded-detection}
Detection cascades \cite{Viola-IJCV-2004,Felzenszwalb-CVPR-2010} are a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers.
This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip some evaluations \cite{Benbouzid-ICML-2012}.
Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{Sun-CVPR-2013} as well as a boosted cascade trained on CNN features \cite{Zou-BMVC-2014}. While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,DulacArnold-ICLR-2014}.
